Homework 8

### 2019-11-05 hw8/MSimonsHW8.tex
hw8 problem 1a

>>>>

\item
\begin{enumerate}

\item Since $(x^7 + 25x^6 - 25x + 5)$ is a nonconstant polynomial in
$\mathbb{Q}$, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field if and only if
$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$.  We know that
$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$ by Eisenstein's
Criterion for prime $5$.  Thus, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field.

\item TODO
\item TODO

\end{enumerate}
